\documentclass[letter,10pt]{article}
\usepackage[utf8]{inputenc}

%====================
% OFFICIAL PUBLIC OVERLEAF TEMPLATE
% https://www.overleaf.com/latex/templates/data-science-tech-resume-template/zcdmpfxrzjhv
% 
%====================
%
% Resume template for data scientists, a complement to data-science-tech-cover-letter-template:
% https://www.overleaf.com/latex/templates/data-science-tech-cover-letter-template/gbrcqktbsfxf
%
% Files:        resume.tex: Main file
%               _header.tex: header code
%               TLCresume.sty: style file containing formatting details
%               section/objective: https://www.indeed.com/career-advice/resumes-cover-letters/resume-objective-examples
%               section/skills: table of skills
%               section/experience: projects or roles
%               section/education: schools and stuff
%               section/activities: optional, could comment out in resume.tex.
%
% Editor:       https://github.com/TimmyChan
%               https://www.linkedin.com/in/timmy-l-chan/
%               
% Last Updated: March 24th, 2022
%  
%====================
 
\usepackage{hyperref}
\usepackage{TLCresume}
%  
%==================== 
% CONTACT INFORMATION
%====================
\def\name{Renaud DUBOIS} % Name Here
%\def\phone{(+33) 6.51.09.18.05}
\def\phone{(+33) 6.XX.XX.XX.XX}
\def\city{Paris, France}
\def\email{prenom.nom@monentreprise.fr}
\def\LinkedIn{renaud-dubois-63a62411} % linkedin.com/in/______
\def\github{rdubois-crypto} % github username
\def\role{Senior Cryptographer\\ Innovation Leader} % JOB TITLE

\input{_header}
\begin{document}
\input{sections/objective}

\section{Skills}
\input{sections/skills}

\section{Technical Experience}
\input{sections/experience}

\section{Education}
\input{sections/education}

% make a newpage wherever it is a clean break
% \newpage

\section{Activities}
\input{sections/activities}
 
\section{Brevets (extract)}
\url{https://www.patentguru.com/inventor/dubois-renaud}

The final name of the patent may differ from the original technical text once chewed by the IP teams. Last sentences give the real patent aim.
 \begin{enumerate}
  \item  Renaud Dubois, David Lefranc, Matthieu Walle, MKD-Procédé de chiffrement hybride multi-contenus et multi-destinataires. Merklelization, and multi content signature for efficient software updates.
  \item Renaud Dubois, Eric Garrido, Olivier Bernard, Alexandre Anzala, Anne-Rose Gratadour, Solution d'intégrité au niveau trame pour un système de diffusion possiblement sans voie de retour.
  \item Renaud Dubois, Olivier Bernard EC4 - Procédé de génération des paramètres caractérisant un protocole cryptographique. 2016. ( dépôt N1601067). Génération transparente de paramètres elliptiques.
 \item Renaud Dubois, Aurélien Dupin, Julien Prat, Thomas Ricosset. METHOD FOR SECURING THE BALANCE OF AN ELECTRONIC ACCOUNT.\url{https://www.patentguru.com/EP3843324A1}. Décrit comment réaliser un bitcoin post quantique et une méthode de transition via commitment d'une chain à l'autre.
 \item Renaud Dubois, Aurore Guillevic, Damien Vergnaud. Method for generating session key from secret key and public parameter by cryptography unit, involves deducing session key from value received from calculating unit, where value is value of binary function applied to data from tokens. 2018. Elliptic Pairing computation Delegation.
 \item  METHOD OF IDENTIFYING A PROTOCOL GIVING RISE TO A DATA FLOW. Techniques de machine learning appliquées à la détection d'intrusion.
 \end{enumerate}  
  
\section{Publications}
 \url{https://dblp.org/pid/26/211.html}
 \begin{enumerate}
  \item Abdessamad Fazzat, Rida Khatoun, Houda Labiod, Renaud Dubois: A comparative performance study of cryptographic algorithms for connected vehicles. 2020.
 \item 	Olivier Bernard, Renaud Dubois, Simon Masson: Efficient four-dimensional GLV curve with high security.
 \item Renaud Dubois: Trapping ECC with Invalid Curve Bug Attacks. 
 \item Renaud Dubois, Margaux Dugardin, Aurore Guillevic: Golden Sequence for the PPSS Broadcast Encryption Scheme with an Asymmetric Pairing.
 \item Renaud Dubois, Aurore Guillevic, Marine Sengelin Le Breton:
Improved Broadcast Encryption Scheme with Constant-Size Ciphertext. Pairing 2012. 
\item Fabien Allard, Mathieu Morel, Renaud Dubois et Paul Gompel. CASTAFIOR : Tunneling activities detection using machine learning techniques. JTIT2010, Journal of Telecommunications and Information Technology. 
 \item 	Guillaume Fumaroli, Emmanuel Mayer, Renaud Dubois:
First-Order Differential Power Analysis on the Duplication Method. INDOCRYPT 2007.
 \end{enumerate} 
 
   
\end{document}
